Digitization of the Australian Parliamentary Debates, 1998-2022

### 2023-07-03 paper/paper-nature-revised.qmd
more paper revisions

> ```{r}
> #| warning: false
> #| echo: false
> #| message: false
> #| results: asis
> >
> # read in XML file
> raw_ex <-  xmlParse("/Volumes/Verbatim/input/2021-11-30.xml")
> >
> # extract example of text (chose this one b/c it's short and has an interruption by The Speaker)
> interject_text_ex <- cbind(xmlToDataFrame(node=getNodeSet(raw_ex, "//chamber.xscript/debate/subdebate.1/speech/talk.start/talker")),
>                            xmlToDataFrame(node=getNodeSet(raw_ex, "//chamber.xscript/debate/subdebate.1/speech/talk.text"))) %>% 
>   as_tibble() %>% 
>   slice(25) %>% 
>   pull(body)
> >
> # print example of text in quotations
> cat(paste0('"', interject_text_ex, '"'))
> ```

@@

Our database is available in both CSV and parquet formats. It covers all sitting days of the House of Representatives from 02 March 1998 to 08 September 2022, so there are **1,527 individual sitting day** files for each format. **Additionally, there is a single corpus file in both CSV and Parquet forms containing the data from all sitting days, with a date variable added to allow for distinction and filtering of individual sitting days. There is also a CSV and Parquet file containing all parsed debate topics.** All data records are available on the general-purpose repository Zenodo, at https://doi.org/10.5281/zenodo.7799678 [@katz_2023]. For each **Hansard data** file, **that is, the corpus and the individual sitting day files**, each row contains an individual statement, with details on the individual speaking. For general statements transcribed as made by "Honourable members" for example, these variables cannot be specified. @tbl-vars provides an overview of each variable found in the **Hansard data files in the** database.

@@

The `name`, `page.no`, `time.stamp`, `name.id`, `electorate`, `party`, `in.gov`, `first.speech`, and `body` variables all came directly from the XML contents. In addition to these variables, we added a number of flags to enable easy filtering of statements. For example, adding the `fedchamb_flag` provides a clear distinction between the proceedings of the Chamber with those of the Federation Chamber. The `question`, `answer`, and `q_in_writing` flags were added to identify statements belonging to Question Time, and the nature of these statements. We also flagged for interjections (`interject`), and the `div_flag` variable was added to flag when a division is called for. The `gender` and `uniqueID` variables were added based on the main dataset from the `AustralianPoliticians` package, **and the `partyfacts_id` variable was added using code and data provided by the Party Facts Project [website](https://partyfacts.herokuapp.com).**[^3] Details on the usage of `uniqueID` **and `partyfacts_id`** will be provided in @sec-usage. Further, the `speech_no` variable allows us to keep track of the speech number that each statement and interjection belongs to. Having the speech number variable offers an easy way to group statements by speech or isolate specific speeches of interest. **Lastly, the `order` variable was added to maintain the order of proceedings, after all individual statements were separated onto their own rows.**

[^3]: **Note that in accordance with the code provided on the Party Facts \[downloads page\](https://partyfacts.herokuapp.com/download/), we used only the core datasets maintained by the Party Facts project, which are the Manifesto Project and ParlGov. Details on these datasets can be found here: https://partyfacts.herokuapp.com/documentation/datasets/.**

@@

**Finally, there is a CSV file in our database called `PartyFacts_map.csv`. This file was created using `AustralianPoliticians` data, data downloaded from the Party Facts project, and our own Hansard data `party` variable. As there are some party name and abbreviation spelling inconsistencies across these sources, creating this dataframe allowed us to ensure correct merging of PartyFacts ID numbers with their associated party, in accordance with the party abbreviation spelling transcribed in our Hansard data. Further, we included the corresponding party abbreviation and full name spelling found in the `AustralianPoliticians` package data in this dataframe for completeness.**

@@

pf_vars <- tibble("Variable" = c("partyfacts_id",
                                 "party_abb_hansard",
                                 "party_abb_auspol",
                                 "party_name_auspol"),
                  "Description" = c("PartyFacts identification number, based on linked parties data from the Party Facts project",
                                    "Party abbreviation as transcribed in the Hansard data",
                                    "Party abbreviation as recorded in the `AustralianPoliticians` data",
                                    "Party full name as recorded in the `AustralianPoliticians` data"))

@@

The second test is designed to test for duplication errors in the data, by checking whether two lines that immediately follow each other have the same body (i.e. spoken content). This test detected **130** dates on which duplicate statements were made, and one immediately follows the other. Note that this test does not account for who is making each statement, meaning one MP repeating the words of another MP would be picked up in this test as well. We checked a sample of 40% of these duplicates, and manually validated that they are all repeated statements that do exist and are transcribed closely together in that day's XML file, and by our method should be parsed such that one of these statements is immediately followed by the other.

@@

>>>>

> ```{r, eval = F, echo=F}
> # pasting text in directly to avoid issues with rendering.
> #| warning: false
> #| echo: false
> #| message: false
> #| results: asis
> >
> # read in XML file
> raw_ex <-  xmlParse("/Volumes/Verbatim/input/2021-11-30.xml")
> >
> # extract example of text (chose this one b/c it's short and has an interruption by The Speaker)
> interject_text_ex <- cbind(xmlToDataFrame(node=getNodeSet(raw_ex, "//chamber.xscript/debate/subdebate.1/speech/talk.start/talker")),
>                            xmlToDataFrame(node=getNodeSet(raw_ex, "//chamber.xscript/debate/subdebate.1/speech/talk.text"))) %>% 
>   as_tibble() %>% 
>   slice(25) %>% 
>   pull(body)
> >
> # print example of text in quotations
> cat(paste0('"', interject_text_ex, '"'))
> ```

> "Mr VAN MANEN (Forde---Chief Government Whip) (13:59): It's a great pleasure to share with the House that Windaroo Valley State High School has qualified for the finals of the Australian Space Design Competition, to begin in January next year. The competition is regarded as the premier STEM competition for high school students and is recognised by universities around the country. The students are required to respond to industry-level engineering and requests for tender for design and---The SPEAKER: Order! In accordance with standing order 43, the time for members' statements has concluded."

@@

Our database is available in both CSV and parquet formats. It covers all sitting days of the House of Representatives from 02 March 1998 to 08 September 2022 **where an XML transcript is available**, so there are **1,532 individual sitting day** files for each format. **Additionally, there is a single corpus file in both CSV and Parquet forms containing the data from all sitting days, with a date variable added to allow for distinction and filtering of individual sitting days. There is also a CSV and Parquet file containing all parsed debate topics.** All data records are available on the general-purpose repository Zenodo, at https://doi.org/10.5281/zenodo.7799678 [@katz_2023]. For each **Hansard data** file, **that is, the corpus and the individual sitting day files**, each row contains an individual statement, with details on the individual speaking. For general statements transcribed as made by "Honourable members" for example, these variables cannot be specified. @tbl-vars provides an overview of each variable found in the **Hansard data files in the** database.

@@

The `name`, `page.no`, `time.stamp`, `name.id`, `electorate`, `party`, `in.gov`, `first.speech`, and `body` variables all came directly from the XML contents. In addition to these variables, we added a number of flags to enable easy filtering of statements. For example, adding the `fedchamb_flag` provides a clear distinction between the proceedings of the Chamber with those of the Federation Chamber. The `question`, `answer`, and `q_in_writing` flags were added to identify statements belonging to Question Time, and the nature of these statements. We also flagged for interjections (`interject`), and the `div_flag` variable was added to flag **those rows where "The House divided." was detected in the body variable**. The `gender` and `uniqueID` variables were added based on the main dataset from the `AustralianPoliticians` package, **and the `partyfacts_id` variable was added using code and data provided by the Party Facts Project [website](https://partyfacts.herokuapp.com).**[^3] Details on the usage of `uniqueID` **and `partyfacts_id`** will be provided in @sec-usage. Further, the `speech_no` variable allows us to keep track of the speech number that each statement and interjection belongs to. Having the speech number variable offers an easy way to group statements by speech or isolate specific speeches of interest. **Lastly, the `order` variable was added to maintain the order of proceedings, after all individual statements were separated onto their own rows.**

[^3]: **Note that in accordance with the code provided on the Party Facts [downloads page](https://partyfacts.herokuapp.com/download/), we used only the core datasets maintained by the Party Facts project, which are the Manifesto Project and ParlGov. Details on these datasets can be found here: https://partyfacts.herokuapp.com/documentation/datasets/.**

@@

**Finally, there is a CSV file in our database called `PartyFacts_map.csv`. This file was created using `AustralianPoliticians` data, data downloaded from the Party Facts project, and our own Hansard data `party` variable. As there are some party name and abbreviation spelling inconsistencies across these sources, creating this dataframe allowed us to ensure correct merging of PartyFacts ID numbers with their associated party, in accordance with the party abbreviation spelling transcribed in our Hansard data. Further, we included the corresponding party abbreviation and full name spelling found in the `AustralianPoliticians` package for completeness.**

@@

pf_vars <- tibble("Variable" = c("partyfacts_id",
                                 "party_abb_hansard",
                                 "party_abb_auspol",
                                 "party_name_auspol"),
                  "Description" = c("PartyFacts identification number, based on linked parties data from the Party Facts project",
                                    "Party abbreviation as transcribed in the Hansard data",
                                    "Party abbreviation as recorded in the AustralianPoliticians R package data",
                                    "Party full name as recorded in the AustralianPoliticians R package data"))

@@

The second test is designed to test for duplication errors in the data, by checking whether two lines that immediately follow each other have the same body (i.e. spoken content). This test detected **131** dates on which duplicate statements were made, and one immediately follows the other. Note that this test does not account for who is making each statement, meaning one MP repeating the words of another MP would be picked up in this test as well. We checked a sample of 40% of these duplicates, and manually validated that they are all repeated statements that do exist and are transcribed closely together in that day's XML file, and by our method should be parsed such that one of these statements is immediately followed by the other.

@@

## Summary Statistics

**To further explore the quality of our data and detect any unexpected or distinct trends, we generated a number of summary statistics using the complete Hansard corpus. First, we looked at the number of speeches made each day, disaggregated by Chamber and Federation Chamber debate venues. As shown in @fig-dailyspeeches, there are consistently more speeches made in the Chamber proceedings than in the Federation Chamber, which aligns with the wider scope of business covered in the Chamber. Further, in both debate venues, the number of speeches each day appears to have increased slightly over time.**

![Number of speeches made on each sitting day in the House of Representatives](n_daily_speeches.png){#fig-dailyspeeches width="440"}

**Next, we explored the number of unique names detected on each sitting day disaggregated by debate venue, visualized in @fig-names. As expected, there are generally more individual MPs detected to be present in the Chamber proceedings in our data than in the Federation Chamber proceedings. Further, in both venues, the number of individuals detected per sitting day appears to have increased since around 2008-2009, with a maximum of 116 and 87 unique names detected for the Chamber and Federation Chamber, respectively. Across the time frame of our data, there was a daily average of 84 unique names detected in the Chamber, and 34 in the Federation Chamber. These observations are in accordance with the official number of Members belonging to the House of Representatives, which was 148 in 1998, 150 in 2001, and then increased to 151 in the 2019 general election [@australia2018house].**

![Daily number of unique names detected in our Hansard data](n_unique_names.png){#fig-names width="440"}

**We then computed the total number of speeches made in our database by political party, summarized in @tbl-speeches_by_party. We found that the Australian Labor Party made the most speeches overall, followed by the Liberal Party of Australia, and the Nationalist Party. These rankings are unsurprising, as those parties are the three main political parties in the Australian House of Representatives [@infosheet_parties].**

```{r}
#| warning: false
#| message: false
#| echo: false
#| label: tbl-speeches_by_party
#| tbl-cap: "Total number of speeches made in our database by political party"
read_csv("s_by_party_name.csv", show_col_types = F) |> 
  knitr::kable(booktabs=T) |> 
  kableExtra::kable_styling(full_width = F, latex_options = "HOLD_position")
#### check NAT vs NPA full names - are these correct? google is confusing me
```

### 2023-07-03 paper/paper-nature-revised.tex
more paper revisions

\title{Digitization of the Australian Parliamentary Debates, 1998-2022}
\author{Lindsay Katz\footnote{University of Toronto,
  lindsay.katz@mail.utoronto.ca} \and Rohan Alexander\footnote{University
  of Toronto, rohan.alexander@utoronto.ca}}
\date{June 29, 2023}

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro- and micro-level text analysis because it has only
been available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures
proceedings of the Australian parliamentary debates from 1998 to 2022.
The database is publicly available and can be linked to other datasets
such as election results. The creation and accessibility of this
database enables the exploration of new questions and serves as a
valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, frame hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners, interior hidden, enhanced, breakable]}{\end{tcolorbox}}\fi

@@

@@

Our database is available in both CSV and parquet formats. It covers all
sitting days of the House of Representatives from 02 March 1998 to 08
September 2022, so there are 1,517 \textbf{individual sitting day} files
for each format. \textbf{Additionally, there is a single corpus file in
both CSV and Parquet forms containing the data from all sitting days,
with a date variable added to allow for distinction and filtering of
individual sitting days. There is also a CSV and Parquet file containing
all parsed debate topics.} All data records are available on the
general-purpose repository Zenodo, at
https://doi.org/10.5281/zenodo.7799678 (Katz and Alexander 2023). For
each \textbf{Hansard data} file, \textbf{that is, the corpus and the
individual sitting day files}, each row contains an individual
statement, with details on the individual speaking. For general
statements transcribed as made by ``Honourable members'' for example,
these variables cannot be specified. Table~\ref{tbl-vars} provides an
overview of each variable found in the \textbf{Hansard data files in
the} database.

@@

The \texttt{name}, \texttt{page.no}, \texttt{time.stamp},
\texttt{name.id}, \texttt{electorate}, \texttt{party}, \texttt{in.gov},
\texttt{first.speech}, and \texttt{body} variables all came directly
from the XML contents. In addition to these variables, we added a number
of flags to enable easy filtering of statements. For example, adding the
\texttt{fedchamb\_flag} provides a clear distinction between the
proceedings of the Chamber with those of the Federation Chamber. The
\texttt{question}, \texttt{answer}, and \texttt{q\_in\_writing} flags
were added to identify statements belonging to Question Time, and the
nature of these statements. We also flagged for interjections
(\texttt{interject}), and the \texttt{div\_flag} variable was added to
flag when a division is called for. The \texttt{gender} and
\texttt{uniqueID} variables were added based on the main dataset from
the \texttt{AustralianPoliticians} package, \textbf{and the
\texttt{partyfacts\_id} variable was added using code and data provided
by the Party Facts Project
\href{https://partyfacts.herokuapp.com}{website}.}\footnote{\textbf{Note
  that in accordance with the code provided on the Party Facts
  {[}downloads page{]}(https://partyfacts.herokuapp.com/download/), we
  used only the core datasets maintained by the Party Facts project,
  which are the Manifesto Project and ParlGov. Details on these datasets
  can be found here:
  https://partyfacts.herokuapp.com/documentation/datasets/.}} Details on
the usage of \texttt{uniqueID} \textbf{and \texttt{partyfacts\_id}} will
be provided in Section~\ref{sec-usage}. Further, the \texttt{speech\_no}
variable allows us to keep track of the speech number that each
statement and interjection belongs to. Having the speech number variable
offers an easy way to group statements by speech or isolate specific
speeches of interest. \textbf{Lastly, the \texttt{order} variable was
added to maintain the order of proceedings, after all individual
statements were separated onto their own rows.}

@@

\textbf{Finally, there is a CSV file in our database called
\texttt{PartyFacts\_map.csv}. This file was created using
\texttt{AustralianPoliticians} data, data downloaded from the Party
Facts project, and our own Hansard data \texttt{party} variable. As
there are some party name and abbreviation spelling inconsistencies
across these sources, creating this dataframe allowed us to ensure
correct merging of PartyFacts ID numbers with their associated party, in
accordance with the party abbreviation spelling transcribed in our
Hansard data. Further, we included the corresponding party abbreviation
and full name spelling found in the \texttt{AustralianPoliticians}
package data in this dataframe for completeness.}

@@

\centering
\begin{tabular}{>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{25em}}
\toprule
Variable & Description\\
\midrule
partyfacts\_id & PartyFacts identification number, based on linked parties data from the Party Facts project\\
party\_abb\_hansard & Party abbreviation as transcribed in the Hansard data\\
party\_abb\_auspol & Party abbreviation as recorded in the `AustralianPoliticians` data\\
party\_name\_auspol & Party full name as recorded in the `AustralianPoliticians` data\\
\bottomrule
\end{tabular}
\end{table}

@@

The second test is designed to test for duplication errors in the data,
by checking whether two lines that immediately follow each other have
the same body (i.e.~spoken content). This test detected 129 dates on
which duplicate statements were made, and one immediately follows the
other. Note that this test does not account for who is making each
statement, meaning one MP repeating the words of another MP would be
picked up in this test as well. We checked a sample of 40\% of these
duplicates, and manually validated that they are all repeated statements
that do exist and are transcribed closely together in that day's XML
file, and by our method should be parsed such that one of these
statements is immediately followed by the other.

@@

@@

To enhance the usability of our database, we added a \texttt{uniqueID}
variable to each file. This serves as a unique identifier for each
speaking MP, and comes from the \texttt{uniqueID} variable present
within data from both the \texttt{AustralianPoliticians} and
\texttt{AustralianElections} R packages (Alexander and Hodgetts 2021;
Alexander 2019). By including this variable, one can readily integrate
our data records with those available in these two packages.
\textbf{Similarly, we added the \texttt{partyfacts\_id} variable to our
data which allows users to link our data to external political party
information.}

@@

>>>>

\title{Digitization of the Australian Parliamentary Debates, 1998-2022}
\author{Lindsay Katz\footnote{University of Toronto,
  lindsay.katz@mail.utoronto.ca} \and Rohan Alexander\footnote{University
  of Toronto, rohan.alexander@utoronto.ca}}
\date{July 3, 2023}

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro- and micro-level text analysis because it has only
been available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures
proceedings of the Australian parliamentary debates from 1998 to 2022.
The database is publicly available and can be linked to other datasets
such as election results. The creation and accessibility of this
database enables the exploration of new questions and serves as a
valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, frame hidden, interior hidden, enhanced, boxrule=0pt, sharp corners, borderline west={3pt}{0pt}{shadecolor}]}{\end{tcolorbox}}\fi

@@

\begin{quote}
\end{quote}

@@

Our database is available in both CSV and parquet formats. It covers all
sitting days of the House of Representatives from 02 March 1998 to 08
September 2022 \textbf{where an XML transcript is available}, so there
are \textbf{1,532 individual sitting day} files for each format.
\textbf{Additionally, there is a single corpus file in both CSV and
Parquet forms containing the data from all sitting days, with a date
variable added to allow for distinction and filtering of individual
sitting days. There is also a CSV and Parquet file containing all parsed
debate topics.} All data records are available on the general-purpose
repository Zenodo, at https://doi.org/10.5281/zenodo.7799678 (Katz and
Alexander 2023). For each \textbf{Hansard data} file, \textbf{that is,
the corpus and the individual sitting day files}, each row contains an
individual statement, with details on the individual speaking. For
general statements transcribed as made by ``Honourable members'' for
example, these variables cannot be specified. Table~\ref{tbl-vars}
provides an overview of each variable found in the \textbf{Hansard data
files in the} database.

@@

The \texttt{name}, \texttt{page.no}, \texttt{time.stamp},
\texttt{name.id}, \texttt{electorate}, \texttt{party}, \texttt{in.gov},
\texttt{first.speech}, and \texttt{body} variables all came directly
from the XML contents. In addition to these variables, we added a number
of flags to enable easy filtering of statements. For example, adding the
\texttt{fedchamb\_flag} provides a clear distinction between the
proceedings of the Chamber with those of the Federation Chamber. The
\texttt{question}, \texttt{answer}, and \texttt{q\_in\_writing} flags
were added to identify statements belonging to Question Time, and the
nature of these statements. We also flagged for interjections
(\texttt{interject}), and the \texttt{div\_flag} variable was added to
flag \textbf{those rows where ``The House divided.'' was detected in the
body variable}. The \texttt{gender} and \texttt{uniqueID} variables were
added based on the main dataset from the \texttt{AustralianPoliticians}
package, \textbf{and the \texttt{partyfacts\_id} variable was added
using code and data provided by the Party Facts Project
\href{https://partyfacts.herokuapp.com}{website}.}\footnote{\textbf{Note
  that in accordance with the code provided on the Party Facts
  \href{https://partyfacts.herokuapp.com/download/}{downloads page}, we
  used only the core datasets maintained by the Party Facts project,
  which are the Manifesto Project and ParlGov. Details on these datasets
  can be found here:
  https://partyfacts.herokuapp.com/documentation/datasets/.}} Details on
the usage of \texttt{uniqueID} \textbf{and \texttt{partyfacts\_id}} will
be provided in Section~\ref{sec-usage}. Further, the \texttt{speech\_no}
variable allows us to keep track of the speech number that each
statement and interjection belongs to. Having the speech number variable
offers an easy way to group statements by speech or isolate specific
speeches of interest. \textbf{Lastly, the \texttt{order} variable was
added to maintain the order of proceedings, after all individual
statements were separated onto their own rows.}

@@

\textbf{Finally, there is a CSV file in our database called
\texttt{PartyFacts\_map.csv}. This file was created using
\texttt{AustralianPoliticians} data, data downloaded from the Party
Facts project, and our own Hansard data \texttt{party} variable. As
there are some party name and abbreviation spelling inconsistencies
across these sources, creating this dataframe allowed us to ensure
correct merging of PartyFacts ID numbers with their associated party, in
accordance with the party abbreviation spelling transcribed in our
Hansard data. Further, we included the corresponding party abbreviation
and full name spelling found in the \texttt{AustralianPoliticians}
package for completeness.}

@@

\centering
\begin{tabular}{>{\raggedright\arraybackslash}p{10em}>{\raggedright\arraybackslash}p{25em}}
\toprule
Variable & Description\\
\midrule
partyfacts\_id & PartyFacts identification number, based on linked parties data from the Party Facts project\\
party\_abb\_hansard & Party abbreviation as transcribed in the Hansard data\\
party\_abb\_auspol & Party abbreviation as recorded in the AustralianPoliticians R package data\\
party\_name\_auspol & Party full name as recorded in the AustralianPoliticians R package data\\
\bottomrule
\end{tabular}
\end{table}

@@

The second test is designed to test for duplication errors in the data,
by checking whether two lines that immediately follow each other have
the same body (i.e.~spoken content). This test detected \textbf{131}
dates on which duplicate statements were made, and one immediately
follows the other. Note that this test does not account for who is
making each statement, meaning one MP repeating the words of another MP
would be picked up in this test as well. We checked a sample of 40\% of
these duplicates, and manually validated that they are all repeated
statements that do exist and are transcribed closely together in that
day's XML file, and by our method should be parsed such that one of
these statements is immediately followed by the other.

@@

\hypertarget{summary-statistics}{%
\subsection{Summary Statistics}\label{summary-statistics}}

\textbf{To further explore the quality of our data and detect any
unexpected or distinct trends, we generated a number of summary
statistics using the complete Hansard corpus. First, we looked at the
number of speeches made each day, disaggregated by Chamber and
Federation Chamber debate venues. As shown in
Figure~\ref{fig-dailyspeeches}, there are consistently more speeches
made in the Chamber proceedings than in the Federation Chamber, which
aligns with the wider scope of business covered in the Chamber. Further,
in both debate venues, the number of speeches each day appears to have
increased slightly over time.}

{\centering \includegraphics[width=4.58333in,height=\textheight]{n_daily_speeches.png}

\caption{\label{fig-dailyspeeches}Number of speeches made on each
sitting day in the House of Representatives}

\textbf{Next, we explored the number of unique names detected on each
sitting day disaggregated by debate venue, visualized in
Figure~\ref{fig-names}. As expected, there are generally more individual
MPs detected to be present in the Chamber proceedings in our data than
in the Federation Chamber proceedings. Further, in both venues, the
number of individuals detected per sitting day appears to have increased
since around 2008-2009, with a maximum of 116 and 87 unique names
detected for the Chamber and Federation Chamber, respectively. Across
the time frame of our data, there was a daily average of 84 unique names
detected in the Chamber, and 34 in the Federation Chamber. These
observations are in accordance with the official number of Members
belonging to the House of Representatives, which was 148 in 1998, 150 in
2001, and then increased to 151 in the 2019 general election (House of
Representatives 2018).}

{\centering \includegraphics[width=4.58333in,height=\textheight]{n_unique_names.png}

\caption{\label{fig-names}Daily number of unique names detected in our
Hansard data}

\textbf{We then computed the total number of speeches made in our
database by political party, summarized in
Table~\ref{tbl-speeches_by_party}. We found that the Australian Labor
Party made the most speeches overall, followed by the Liberal Party of
Australia, and the Nationalist Party. These rankings are unsurprising,
as those parties are the three main political parties in the Australian
House of Representatives (Parliament of Australia 2022).}

\hypertarget{tbl-speeches_by_party}{}
\begin{table}[H]
\caption{\label{tbl-speeches_by_party}Total number of speeches made in our database by political party }\tabularnewline

\centering
\begin{tabular}{llr}
\toprule
Party Name & Party Abbreviation & Total \# of Speeches\\
\midrule
Australian Labor Party & ALP & 112268\\
Liberal Party of Australia & LIB & 106139\\
Nationalist Party & NAT & 15799\\
Independent & IND & 5357\\
National Party of Australia & NPA & 4580\\
\addlinespace
Australian Greens & GRN & 1446\\
Country Liberal Party (Northern Territory) & CLP & 665\\
Centre Alliance & CA & 638\\
Katters Australian Party & KAP & 263\\
Nick Xenophon Team & NXT & 186\\
\addlinespace
National Party of Australia (WA) & NATS WA & 68\\
Palmer United Party & PUP & 64\\
United Australia Party & UAP & 43\\
\bottomrule
\end{tabular}
\end{table}

@@

To enhance the usability of our database, we added a \texttt{uniqueID}
variable to each file. This serves as a unique identifier for each
speaking MP, and comes from the \texttt{uniqueID} variable present
within data from both the \texttt{AustralianPoliticians} and
\texttt{AustralianElections} R packages (Alexander and Hodgetts 2021;
Alexander 2019). By including this variable, one can readily integrate
our data records with those available in these two packages.
\textbf{Similarly, we added the \texttt{partyfacts\_id} variable to our
data which allows users to link our data to external political party
data sources with this unique identifier.}

@@

\leavevmode\vadjust pre{\hypertarget{ref-infosheet_parties}{}}%
Parliament of Australia. 2022. {``Infosheet 22 - Political Parties.''}
\emph{House of Representatives Infosheets}.
\url{https://www.aph.gov.au/About_Parliament/House_of_Representatives/Powers_practice_and_procedure/00_-_Infosheets/Infosheet_22_-_Political_parties}.
